%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[T1]{fontenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{lmodern}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks=true, linkcolor=blue, urlcolor=NavyBlue, bookmarks=false, pdfencoding=auto, psdextra]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
	\item\small{
		{#1 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
	\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
	\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\small#1 & #2 \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
	
	\begin{center}
		\textbf{\Huge Hemal Patel} \\ \vspace{1pt}
		\small Horsham, PA $|$ 908-300-4557 $|$ \nolinkurl{hemalpatel2990@hotmail.com} $|$
		\href{https://linkedin.com/in/hemalpatel2990}{LinkedIn} $|$
		\href{https://hemalpatel2990.github.io/}{Portfolio}
	\end{center}
	
	%----------- PROFESSIONAL SUMMARY-----------
	\section*{Professional Summary}
	\addcontentsline{toc}{section}{Professional Summary}
	\small {Senior Engineer with 10+ years shipping gameplay systems, multiplayer networking, and engine tooling in UE5 and Unity. Solo-architected a production multiplayer networking system; recovered frame rate from 15fps to 36fps via Niagara system overhaul; built CI/CD build pipeline tooling adopted studio-wide. Led cross-discipline teams across PC, mobile, and XR. Equally strong in gameplay engineering and engine tools --- and the profiling sessions nobody else wants to run.}
	
	
	%-----------PROGRAMMING SKILLS-----------
	\section*{Skills}
	\addcontentsline{toc}{section}{Skills}
	\begin{itemize}[leftmargin=0.15in, label={}]
		\small{\item{
				\textbf{Languages}{: C++, C\symbol{35}, Lua, Python} \\
				\textbf{Engines \& Frameworks}{: Unreal Engine 4/5 (Blueprints, GAS, Niagara, Unreal Insights), Unity, Godot} \\
				\textbf{Gameplay Engineering}{: Multiplayer Networking, Server-Authoritative Architecture, Gameplay Systems, Real-Time Interactive Systems, Multithreading, Performance Profiling \& Optimization} \\
				\textbf{Tools \& Pipeline}{: Editor Tools \& Build Automation, CI/CD, Custom PAK Pipelines, RenderDoc, Git, Perforce, BuildGraph, Docker, JIRA} \\
				\textbf{Online \& Backend}{: Oculus / Meta XR SDK, NATS Streaming, REST APIs, Cloud Backends (AWS, Azure), Analytics Pipelines (Segment)} \\
		}}
	\end{itemize}
	
	%-----------SHIPPED TITLES-----------
	\section*{Shipped Titles}
	\addcontentsline{toc}{section}{Shipped Titles}
	\begin{itemize}[leftmargin=0.15in, label={}]
		\small{\item{
				\href{https://store.steampowered.com/app/453000/Wave_Beta/}{\textbf{Wave VR}} (Unity) $|$
				\href{https://www.meta.com/experiences/wave-beta/7011698248940643/}{\textbf{Wave Beta}} (Unreal) $|$ \href{https://www.picoxr.com/global/games/wave}{\textbf{Wave Standalone}} (Unreal) $|$ \textbf{Alimentary Avengers} (Unity) \\
				\textbf{Tafe Planetary Plus} (Unity) $|$ \textbf{E-Smart} $|$ \textbf{Be Safe, Be Smart!}
		}}
	\end{itemize}
	
	%-----------EXPERIENCE-----------
	\section*{Experience}
	\addcontentsline{toc}{section}{Experience}
	\resumeSubHeadingListStart
	\resumeSubheading
	{Software Engineer II}{Nov 2019 -- Dec 2025}
	{WaveXR}{Remote (Horsham, PA)}
	\resumeItemListStart
	\resumeItem{Led 2 engineers and 2 tech artists on the Social Experience feature from prototype to production.}
	\resumeItem{Partnered with product managers and technical artists throughout the feature lifecycle, using JIRA to gather requirements, validate mid-build, and adjust scope. Proposed a phased UI approach --- Phase 1 auto-generated 2D, Phase 2 full 3D --- allowing the initial release to ship on time while preserving the long-term vision.}
	\resumeItem{Architected a production networking system (NATS + Unreal) with Manager/Controller/UI pipelines, enabling real-time player control of live stage visuals; shipped the solution and conducted user testing to confirm stability.}
	\resumeItem{Rebuilt the concurrent Niagara particle system using the command pattern, boosting frame rate from 15\,fps to 36\,fps under full audience load, and resolved RPC/Blueprint bottlenecks via Unreal Insights, cutting frame time and memory usage by over 80\%.}
	\resumeItem{Developed a C\symbol{35} UE5 build-config tool (Unreal Build Tool XML) and custom PAK packager, automating credential injection and stripping across 15 environments; the tool was adopted studio-wide in the CI/CD pipeline.}
	\resumeItem{Designed a NATS-based interaction service routing high-frequency performance data server-side, offloading Unreal replication and enabling multi-instance distribution.}
	\resumeItem{Built a UE5 Segment analytics subsystem batching up to 20 timestamped REST events before dispatch, callable from any game system.}
	\resumeItem{Integrated Meta Horizon party and player-blocking via Oculus SDK, with correct mute/unmute propagation across connected players.}
	\resumeItem{Drove Unity to UE5 engine migration, architecting core systems in C++ and maintaining feature parity across the full product stack.}
	\resumeItemListEnd
	
	\resumeSubheading
	{Unity Programmer (Contract)}{Nov 2015 -- Nov 2020}
	{Razor Edge Games}{Remote (Horsham, PA)}
	\resumeItemListStart
	\resumeItem{Engineered core gameplay systems in C\symbol{35}, including turn-based simulation, inventory management, and survival mechanics, architecting clean, extensible code for long-term maintainability.}
	\resumeItem{Architected and implemented the Character Creator system in Unity from concept to completion, handling complex mesh, animation, and UI interactions, which allowed designers to create and iterate on characters more quickly.}
	\resumeItem{Built custom editor tools and extensions that streamlined the content creation pipeline, reducing iteration time for artists and designers.}
	\resumeItem{Debugged complex rendering and visual systems in Unity, resolved mesh-to-spline conflicts, and wrote custom shaders for holographic UI effects, which eliminated visual glitches and improved overall visual fidelity.}
	\resumeItem{Established coding standards and led code reviews to ensure quality and maintainability across a distributed team.}
	\resumeItemListEnd
	
	\resumeSubheading
	{Unity Developer}{Jun 2014 -- March 2015}
	{Smartcloud Infotech Pvt. Ltd.}{Pune, India}
	\resumeItemListStart
	\resumeItem{Developed and shipped multiple interactive commercial applications on mobile platforms using Unity, delivering on strict client requirements and timelines.}
	\resumeItem{Consulted with clients to define project scope, produced detailed technical estimates using multithreading feasibility analysis, and recommended process improvements that shortened development planning.}
	\resumeItem{Implemented and iteratively refined UI/UX and interactive features based on direct client feedback, driving rapid iteration cycles.}
	\resumeItemListEnd
	
	\resumeSubHeadingListEnd
	
	%-----------PROJECTS-----------
	\section*{Technical Projects}
	\addcontentsline{toc}{section}{Technical Projects}
	\resumeSubHeadingListStart
	\resumeProjectHeading
	{\textbf{ElementalArsenal} $|$ \small{C++, Unreal Engine 5, Gameplay Ability System, Editor Tools}}{}
	\resumeItemListStart
	\resumeItem{Engineered a modular gameplay plugin extending \textbf{GAS} to support data-driven equipment pipelines and automated elemental reactions, applying \textbf{vector math and collision logic} for spatial gameplay mechanics.}
	\resumeItem{Built custom \textbf{Editor Tools} to automate asset generation, significantly accelerating the workflow for gameplay designers.}
	\resumeItemListEnd
	\resumeProjectHeading
	{\textbf{UniversalDataSync (NeoDataSync)} $|$ \small{C++, Unreal Engine, Multiplayer}}{}
	\resumeItemListStart
	\resumeItem{Architected an Unreal Engine plugin to streamline replication of arbitrary data structures in multiplayer environments, reducing networking boilerplate for complex \textbf{gameplay states}.}
	\resumeItemListEnd
	\resumeProjectHeading
	{\textbf{NeoThreads} $|$ \small{C++, Unreal Engine, Multithreading}}{}
	\resumeItemListStart
	\resumeItem{Developed a lightweight concurrency framework to offload computationally expensive operations from the Game Thread, improving frame stability and performance for CPU-intensive gameplay systems.}
	\resumeItemListEnd
	\resumeSubHeadingListEnd
	
	%-----------EDUCATION-----------
	\section*{Education}
	\addcontentsline{toc}{section}{Education}
	\resumeSubHeadingListStart
	\resumeSubheading
	{DePaul University}{Online}
	{MS in Computer Game Programming}{In Progress}
	\resumeSubheading
	{CEPT University}{India}
	{Master of Business Administration, Information Technology and Project Management}{2014}
	\resumeSubheading
	{Gujarat Technological University}{India}
	{Bachelor of Technology in Information Technology}{2012}
	\resumeSubHeadingListEnd
	%-------------------------------------------
\end{document}