%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[T1]{fontenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{lmodern}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks=true, linkcolor=blue, urlcolor=NavyBlue, bookmarks=false, pdfencoding=auto, psdextra]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%% 


\begin{document}

\begin{center}
    \textbf{\Huge Hemal Patel} \\ \vspace{1pt}
    \small Horsham, PA $|$ 908-300-4557 $|$ \nolinkurl{hemalpatel2990@hotmail.com} $|$ 
    \href{https://linkedin.com/in/hemalpatel2990}{LinkedIn} $|$
    \href{https://hemalpatel2990.github.io/}{Portfolio}
\end{center}

%----------- PROFESSIONAL SUMMARY-----------
\section*{Professional Summary}
\addcontentsline{toc}{section}{Professional Summary}
\small {Senior Game Programmer with over 10 years of experience \textbf{designing and shipping gameplay systems, engine features, and tools} in Unreal Engine and Unity. Equally strong in \textbf{C++ and C\symbol{35}}, with deep expertise in \textbf{system architecture, 3D math, physics, multiplayer networking, and engine internals}. Proven ability to \textbf{drive technical execution}---including contributing to a full engine migration from Unity to UE5---while collaborating with \textbf{cross-disciplinary teams} across art, design, and audio. Track record of \textbf{shipping production titles} on PC, mobile, and XR platforms. Passionate about clean, performant, and maintainable code across the full game development stack.}


%-----------PROGRAMMING SKILLS-----------
\section*{Skills}
\addcontentsline{toc}{section}{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C++, C\symbol{35}, Lua, Python} \\
     \textbf{Engines \& Frameworks}{: Unreal Engine 4/5, Unity, Godot} \\
     \textbf{Engineering}{: Gameplay Systems, System Architecture, Physics/Collision, Multiplayer Networking, AI \& Behavior Systems, Multithreading, Memory Management} \\
     \textbf{Technical Skills}{: 3D Math \& Linear Algebra, Performance Profiling \& Optimization, Gameplay Prototyping, Rapid Prototyping, CI/CD Pipelines, Automated Testing, Cross-Platform Development (PC, Mobile, XR)} \\
     \textbf{Tools}{: Git, Perforce, Visual Studio, Unreal Insights, RenderDoc, JIRA, BuildGraph, Docker} \\
    }}
 \end{itemize}

%-----------SHIPPED TITLES-----------
\section*{Shipped Titles}
\addcontentsline{toc}{section}{Shipped Titles}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \href{https://www.meta.com/experiences/wave-beta/7011698248940643/}{\textbf{Wave Beta}} (Unreal) $|$ \href{https://www.picoxr.com/global/games/wave}{\textbf{Wave Standalone}} (Unreal) $|$ \textbf{Alimentary Avengers} (Unity) \\
     \textbf{Tafe Planetary Plus} (Unity) $|$ \textbf{E-Smart} $|$ \textbf{Be Safe, Be Smart!}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section*{Experience}
\addcontentsline{toc}{section}{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Engineer II}{Nov 2019 -- Dec 2025}
      {WaveXR}{Remote}
      \resumeItemListStart
        \resumeItem{Played a key role in a major \textbf{engine migration from Unity to Unreal Engine 5}, architecting core systems in C++ and ensuring feature parity across the full product stack.}
        \resumeItem{Led a cross-functional engineering team to develop a core Social Experience, overseeing system design, strategic decision-making, and technical mentorship for junior developers.}
        \resumeItem{Owned large gameplay features end-to-end---from design through implementation and optimization---developing, modifying, and debugging interactive systems in \textbf{C++ and Blueprints}.}
        \resumeItem{Designed and implemented \textbf{server-authoritative networking} architecture, solving complex replication, prediction, and latency challenges for \textbf{multiplayer gameplay} on \textbf{PC, mobile, and XR platforms}.}
        \resumeItem{Defined and enforced \textbf{performance budgets} using \textbf{Unreal Insights} and profiling tools, achieving 80\%+ optimization in memory and frame time on target hardware.}
        \resumeItem{Partnered with \textbf{cross-disciplinary teams} (art, design, audio) to rapidly prototype \textbf{gameplay features}, prioritizing playable iteration to validate requirements early.}
        \resumeItem{Developed custom \textbf{editor tools and build automation} to streamline content pipelines and CI/CD workflows, significantly reducing iteration time across the studio.}
        \resumeItem{Drove \textbf{code review culture} and authored internal technical documentation, improving code quality and onboarding efficiency across a distributed team.}
        \resumeItem{Diagnosed and resolved complex cross-system issues spanning \textbf{physics, animation, networking, and rendering} using systematic debugging and profiling methodologies.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Unity Programmer (Contract)}{Nov 2015 -- Nov 2020}
      {Razor Edge Games}{Remote}
      \resumeItemListStart
        \resumeItem{Engineered core \textbf{gameplay systems} in C\symbol{35}, including turn-based simulation, inventory management, and survival mechanics, architecting clean, extensible code for long-term maintainability.}
        \resumeItem{Collaborated with \textbf{cross-disciplinary teams} to architect and implement the \textbf{Character Creator} system from concept to completion, managing complex mesh, animation, and UI interactions.}
        \resumeItem{Built custom \textbf{editor tools} and extensions that streamlined the content creation pipeline, reducing iteration time for artists and designers.}
        \resumeItem{Debugged complex rendering and visual systems, resolving mesh-to-spline conflicts and implementing \textbf{custom shaders} for holographic UI effects.}
        \resumeItem{Established \textbf{coding standards} and led code reviews to ensure quality and maintainability across a distributed team.}
    \resumeItemListEnd
\pagebreak
    \resumeSubheading
      {Unity Developer}{Jun 2014 -- March 2015}
      {Smartcloud Infotech Pvt. Ltd.}{Pune, India}
      \resumeItemListStart
        \resumeItem{Developed and shipped multiple \textbf{interactive commercial applications} on mobile platforms using Unity, delivering on strict client requirements and timelines.}
        \resumeItem{Consulted with clients to define project scope, provided accurate technical estimations, and recommended process improvements.}
        \resumeItem{Implemented and iteratively refined \textbf{UI/UX and interactive features} based on direct client feedback, driving rapid iteration cycles.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section*{Technical Projects}
\addcontentsline{toc}{section}{Technical Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{ElementalArsenal} $|$ \small{C++, Unreal Engine 5, Gameplay Ability System, Editor Tools}}{}
          \resumeItemListStart
            \resumeItem{Engineered a modular gameplay plugin extending \textbf{GAS} to support data-driven equipment pipelines and automated elemental reactions, applying \textbf{vector math and collision logic} for spatial gameplay mechanics.}
            \resumeItem{Built custom \textbf{Editor Tools} to automate asset generation, significantly accelerating the workflow for gameplay designers.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{UniversalDataSync (NeoDataSync)} $|$ \small{C++, Unreal Engine, Multiplayer}}{}
          \resumeItemListStart
            \resumeItem{Architected an Unreal Engine plugin to streamline replication of arbitrary data structures in multiplayer environments, reducing networking boilerplate for complex \textbf{gameplay states}.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{NeoThreads} $|$ \small{C++, Unreal Engine, Multithreading}}{}
          \resumeItemListStart
            \resumeItem{Developed a lightweight concurrency framework to offload computationally expensive operations from the Game Thread, improving frame stability and performance for CPU-intensive gameplay systems.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section*{Education}
\addcontentsline{toc}{section}{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {DePaul University}{Online}
      {MS in Computer Game Programming} {Coursework Completed (Capstone Pending)}
 \resumeSubheading
      {CEPT University}{India}
      {Master of Business Administration. Information Technology and Project Management}{2014}
 \resumeSubheading
      {Gujarat Technological University}{India}
      {Bachelor of Technology in Information Technology}{2012}
  \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}